RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-31 system.tex
more text

\begin{figure*}
\includegraphics[width=\linewidth]{fig/notebook/notebook.pdf}
\caption{\label{fig:notebook}An RCloud notebook is a sequence of
  \emph{cells}, each a snippet of source in R or Markdown. Notebooks
  are stored in GitHub \emph{gists}, which provide the version-control
  primitives necessary for RCloud.}
\end{figure*}

@@

As we reiterated in 
One of the design goals of the user experience in RCloud

@@

\subsection{Technologies: R, Python, HTML5, interactive notebooks, etc.}

How do we do things that are not trivial to do with IPython (for
example)

What is relationship to a standard CMS with R/Python

dcplot. two-way communication between between backend session and
frontend session.

A key engineering decision in RCloud was to rely on full two-way
communication between the web client human interface, and data and
computing resources in the cloud. It is easier to engineer a design
in which the human interface is pushed one-way from the server
and thereafter all interaction takes place within the client.
Two-way communication is necessary, though, where the size of
the data or computational performance makes it impractical to
move all computation to the client.

>>>>

\begin{figure*}
\includegraphics[width=\linewidth]{fig/notebook/notebook.pdf}
\caption{\label{fig:notebook}An RCloud notebook is a sequence of
  \emph{cells}, each a snippet of source in R or Markdown. Notebooks
  are stored in GitHub \emph{gists}, which provide the version-control
  primitives needed in RCloud during editing (left) or viewing and
  executing (right).}
\end{figure*}

@@

One our main goals is to provide ubiquitous access to the statistical
tools of the R programming language in the wider environment in which data
science teams participate.
%
Given the recent developments of interactive visualization and visual
analytics in HTML5 and the web, we decided to create an
\emph{interconnect} between the two environments.
%
Every RCloud session spawns a new R execution process in a remote
server. The communication between the web browser and the

%% \subsubsection{Object capabilities: R to Javascript RPC and access
%%   control}

HTTP and web services are convenient but much of the protocol is
stateless. (For example, GET requests are required to not change the
remote state, and results can be cached in transparent proxies along
the network). In the case of close communication between a running
R process and a web browser, we seek something that is more flexible
than distinct URLs for every R process (with the resulting
complication in providing access

%% \subsection{Technologies: R, Python, HTML5, interactive notebooks, etc.}

%% How do we do things that are not trivial to do with IPython (for
%% example)

%% What is relationship to a standard CMS with R/Python

%% dcplot. two-way communication between between backend session and
%% frontend session.

%% A key engineering decision in RCloud was to rely on full two-way
%% communication between the web client human interface, and data and
%% computing resources in the cloud. It is easier to engineer a design
%% in which the human interface is pushed one-way from the server
%% and thereafter all interaction takes place within the client.
%% Two-way communication is necessary, though, where the size of
%% the data or computational performance makes it impractical to
%% move all computation to the client.

@@
